---
title: "Cross Validation"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(mgcv)
library(modelr)

library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Step one 

Cross validation "by hand" on simulated data.

runif -> random uniform distribution 
adding runif so that x and y have a non linear relationship

```{r}
set.seed(1)

nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

Let's get this by hand.

can also do train_df %>% arrange(id)to demo that you do not get sequential rows

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")
```

_overlaying your two datasets_ 

```{r}
train_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```


Let's try to fit three models.

- have nothing to do with my testing data

linear model should not be complex enough/ was constructed to not fix;  y = x
smooth = just right; gam function y = smooth function of x (smooth - fit) - treating x as there is some non linearity
wiggly = too wild' breaking the nonlinearity / adding too much nonlinearity k = X = 30, sp = 10e - 6 -- telling you to NOT smooth things --> make sure it is very wiggly

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```


Let's see the results. 

Note: mgcv does smooth fits

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```


```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red") + 
  geom_line(aes(y = pred), color = "red")
```



```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red") + 
  geom_line(aes(y = pred), color = "red")
```
Okay so how would you pick? Graphically clear choice. But now let;s be less subjective (see parameters etc). 


Let's make predictions and compute RMSEs. 

* we are adding predictions / to get fitted values based on the training data --> get rmse
```{r}
test_df %>% add_predictions(linear_mod)
```
#Faster way to get RMSE

- RMSE is prediction error (you want lower)


```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

## Can we iterate ..?

Let's test to see if we can model this again -- is this a fluke

crossv_mc -- does not create a df
it stores a df 
it just changes the row #s 


```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)#do cross validation on my df 100x

cv_df %>% pull(train) %>% .[[1]] #pull out first element of your list of your training dataset


#calling it a class of object resample in which you don't have to keep track of your dataframe and only keep track of which row is in your dataset (gives weird object)--> create into tibble (keeps track of all of your testing splits)

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

# now to fit the model to the data that we are interested in
```

now to fit the models that we care about to the data that we are interested in 


in each dataset i want to fit a lm
and get the rmse that comes out of each lm that comes from the testing dataset

- now here you just use the tibbles 

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) %>% #do cross validation on my df 100x
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble), #this will remove the "resample" tibbles
  ) %>% #now you just got dataframes here (resample the tibbles)
  mutate(
    linear_fits = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_fits = map(.x = train, ~mgcv::gam(y ~ s(x), data = .x)),
    wiggly_fits = map(.x = train, ~mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))
  ) %>% ##each time i fit a lm the training data is changing a little bit corresponding to the first training split and subsequent training split
  mutate(
    rmse_linear = map2_dbl(.x = linear_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_fits, .y = test, ~rmse(model = .x, data = .y)),
  )
```

Make a box plot ...

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

## Try it on a real dataset


```{r}
growth_df = read_csv("data/nepalese_children.csv")
```


```{r}
growth_df %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .3)
```

Brief aside on piecewise linear models.

```{r}
growth_df = 
  growth_df %>% 
  mutate(
    weight_pwl = (weight > 7) * (weight - 7)
  )
```


```{r}
linear_model = lm(armc ~ weight, data = growth_df)
pwl_model = lm(armc ~ weight + weight_pwl, data = growth_df)
smooth_model = mgcv::gam(armc ~ s(weight), data = growth_df)

```



```{r}
growth_df %>% 
  add_predictions(smooth_model) %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .3) + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
cv_df = 
  crossv_mc(growth_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
  )
  

cv_df = 
  cv_df %>% 
  mutate(
    linear_fits = map(.x = train, ~lm(armc ~ weight, data = .x)),
    pwl_fits =    map(.x = train, ~lm(armc ~ weight + weight_pwl, data = .x)),
    smooth_fits = map(.x = train, ~mgcv::gam(armc ~ s(weight), data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_pwl =    map2_dbl(.x = pwl_fits,    .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_fits, .y = test, ~rmse(model = .x, data = .y))
  )
```


Let's look at the results

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```




